---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.path = "figures/"
)
```

# realsat-r

## Dataset Summary

ReaLSAT-R-2.0 provides surface area variations of 15473 reservoirs created after 1984 (detected using satellite imagery analysis, see [paper](http://umnlcc.cs.umn.edu/realsat/reservoirs/data/ReaLSAT-R-2.0.pdf)). In addition, it also provides area variations of 3274 reservoirs created before 1984 (taken from a widely used GRanD database.)

 * 853 reservoirs in ReaLSAT-R-2.0 that are also reported in GRanD dataset.

 * 14620 reservoirs in ReaLSAT-R-2.0 that are not available in GRanD.

 * 3274 reservoirs created before 1984 (taken from GRanD) 

## Exploration

```{r }
library(sf)
library(LAGOSNE)
suppressMessages(library(dplyr))
library(ggplot2)

dt <- read_sf("data/ReaLSAT-R-2.0.shp")

dt_lagosne <- dt %>%
  st_intersects(st_zm(LAGOSNE::lg_extent)) %>%
  lapply(., function(x) length(x)) %>%
  unlist() %>%
  sapply(function(x) x!=0)
dt_lagosne <- dt[dt_lagosne,]

ggplot() +
  geom_sf(data = st_zm(LAGOSNE::lg_extent)) +
  geom_sf(data = dt_lagosne)

dt_lagosne_areas <- dt_lagosne %>%
  st_area() %>%
  units::set_units("ha") %>%
  as.numeric() %>%
  data.frame(area = .)

ggplot(data = dt_lagosne_areas, aes(area)) +
  geom_histogram() +
  scale_x_log10() +
  geom_vline(aes(xintercept = 4))
```

## Links

http://umnlcc.cs.umn.edu/realsat/reservoirs/

http://umnlcc.cs.umn.edu/realsat/reservoirs/data/ReaLSAT-R-2.0.html
